SubsidyExplorer - Step 3: Classify vessels into management regimes

### 2020-08-07 scripts/03_management.Rmd
management

The purpose of this script is to assign management scores to all of our vessels, such that they can later be classified into three different management regimes: 
- Well-managed
- Managed
- Open access

@@

# Make figures?
make_plots <- F

@@

@@

## Assign FMI indicies to regions

@@

  fmi_map <- ggplot()+
    geom_sf(data = world, fill = "black", color = "grey", size = 0.25)+
    geom_sf(data = fmi_map_dat, aes(fill = fmi_best), color = "grey", size = 0.25)+
    theme_bw()+
    scale_fill_distiller(palette = "YlGn", 
                         direction = 1,
                         limits = c(0.2, 1))+
    labs(fill = "FMI Score")

  ggsave(paste0(results_dir, "fmi_score_map.png"), width = 7.5, units = "in")
}
```

@@

# Median F/Fmsy by FAO region
median_fvfmsy_fao <- costello_2016_upsides_dat %>%
  group_by(region_fao_split) %>%
  summarize(fvfmsy_med_region = median(fv_fmsy, na.rm = T),
            fvfmsy_mean_region = mean(fv_fmsy, na.rm = T),
            fvfmsy_w_mean_region = weighted.mean(fv_fmsy, w = msy, na.rm = T)) %>%
  dplyr::select(fao_region = region_fao_split, fvfmsy_med_region)
```

# Median fishing pressure by FAO region and state

```{r}
# median_fvfmsy_fao_flag <- costello_2016_upsides_dat %>%
#   group_by(iso3, region_fao_split) %>%
#   summarize(fvfmsy_med_eez = median(fv_fmsy, na.rm = T),
#             fvfmsy_mean_eez = mean(fv_fmsy, na.rm = T),
#             fvfmsy_w_mean_eez = weighted.mean(fv_fmsy, w = msy, na.rm = T)) %>%
#   dplyr::select(iso3, fao_region = region_fao_split, fvfmsy_med_eez)
```

@@

In order to include flag state, we would need to fix this one - How to treat "multinational" stocks. These should be attributed to all flag states that are fishing in those fisheries.

```{r}
prop_assessed_stocks <- costello_2016_upsides_dat %>%
  group_by(region_fao_split) %>%
  summarize(catch_ram = sum(catch[dbase == "RAM"]),
            catch_other = sum(catch[dbase != "RAM"])) %>%
  mutate(catch_prop_ram = catch_ram/(catch_ram + catch_other)) %>%
  dplyr::select(fao_region = region_fao_split, catch_prop_ram)
```

@@

```{r}
prop_catch_share_stocks <- costello_2016_upsides_dat %>%
  group_by(region_fao_split) %>%
  summarize(catch_share= sum(catch[catch_share == 1]),
            catch_other = sum(catch[catch_share != 1])) %>%
  mutate(catch_prop_cs= catch_share/(catch_share + catch_other)) %>%
  dplyr::select(fao_region = region_fao_split, catch_prop_cs)
```

@@

```{r}
vessel_list_manage <- vessel_list_raw %>%
  left_join(eez_management_indices, by = c("eez_id")) %>%
  left_join(median_fvfmsy_fao, by = c("fao_region")) %>%
  left_join(prop_assessed_stocks, by = c("fao_region")) %>%
  left_join(prop_catch_share_stocks, by = c("fao_region"))

# FAO region 18 is missing stock data, but has some effort
vessel_list_manage$fvfmsy_med_region[is.na(vessel_list_manage$fvfmsy_med_region)] <- 1
vessel_list_manage$catch_prop_ram[is.na(vessel_list_manage$catch_prop_ram)] <- 0
vessel_list_manage$catch_prop_cs[is.na(vessel_list_manage$catch_prop_cs)] <- 0

@@

fvfmsy_quantile <- tibble("indicator" = "fvfmsy") %>%
  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fvfmsy_med_region), nrow = 1)), names(quantile(vessel_list_manage$fvfmsy_med_region))))

catch_ram_quantile <- tibble("indicator" = "catch_prop_ram") %>%
  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$catch_prop_ram), nrow = 1)), names(quantile(vessel_list_manage$catch_prop_ram))))

catch_cs_quantile <- tibble("indicator" = "catch_prop_cs") %>%
  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$catch_prop_cs), nrow = 1)), names(quantile(vessel_list_manage$catch_prop_cs))))

indicator_quantiles <- fmi_quantile %>%
  bind_rows(fvfmsy_quantile) %>%
  bind_rows(catch_ram_quantile) %>%
  bind_rows(catch_cs_quantile)

@@

# Summary plots

## Coorelation between average FMI by flag/fao region and subsidy provisioning

# FMI by flag and FAO from vessel list
fmi_flag_fao <- vessel_list_manage %>%
  group_by(flag) %>%
  mutate(tot_bad_subs = sum(bad_subs),
         tot_fuel_subs = sum(B7_subs)) %>%
  ungroup() %>%
  group_by(flag, fao_region) %>%
  summarize(fmi_weighted_avg = weighted.mean(fmi_best, catch),
            tot_bad_subs = unique(tot_bad_subs),
            tot_fuel_subs = unique(tot_fuel_subs))

ggplot(fmi_flag_fao)+
  aes(x = tot_bad_subs, y = fmi_weighted_avg)+
  geom_point()+
  theme_linedraw()+
  labs(x = "Total capacity-enhancing subsidies (2018 $US)",
       y = "Mean Weighted FMI")+
  scale_y_continuous(limits = c(0,1))+
  scale_x_continuous(labels = comma)

# FMI by flag from vessel list
fmi_flag <- vessel_list_manage %>%
  group_by(flag) %>%
  mutate(tot_bad_subs = sum(bad_subs),
         tot_fuel_subs = sum(B7_subs)) %>%
  ungroup() %>%
  group_by(flag) %>%
  summarize(fmi_weighted_avg = weighted.mean(fmi_best, catch),
            tot_bad_subs = unique(tot_bad_subs),
            tot_fuel_subs = unique(tot_fuel_subs))

ggplot(fmi_flag)+
  aes(x = tot_bad_subs, y = fmi_weighted_avg)+
  geom_point()+
  theme_linedraw()+
  labs(x = "Total capacity-enhancing subsidies (2018 $US)",
       y = "Mean Weighted FMI")+
  scale_y_continuous(limits = c(0,1))+
  scale_x_continuous(labels = comma)

countries_to_highlight <- c("CHN", "USA", "IDN", "JPN", "ISL", "THA")

# FMI by just from Melnychuk et al
fmi_flag_melnychuk_only <- vessel_list_manage %>%
  group_by(flag) %>%
  summarize(tot_bad_subs = sum(bad_subs),
         tot_fuel_subs = sum(B7_subs),
         tot_landings = sum(catch)) %>%
  right_join(melnychuk_2017_mgmt_dat, by = c("flag" = "iso3")) %>%
  mutate(display_name = case_when(flag %in% countries_to_highlight ~ countrycode(flag, "iso3c", "country.name")))

# plot
ggplot(fmi_flag_melnychuk_only)+
  aes(x = tot_bad_subs/1e6, y = fmi_weighted, size = tot_landings/1e6, color = display_name)+
  geom_point()+
  geom_text_repel(aes(label = display_name), size = 4, force = 100, point.padding = 0.25, box.padding = 1)+
  theme_linedraw()+
  labs(x = "Total capacity-enhancing subsidies (million 2018 $US)",
       y = "Weighted FMI")+
  scale_y_continuous(limits = c(0,1))+
  scale_x_continuous(labels = comma)+
  scale_size(range = c(2,8), breaks = c(5,10,15), limits = c(0,15), name = "Marine Capture Production (million mt, 2017)")+
  theme(legend.position = "top")+
  scale_color_discrete(guide = "none")

ggsave(paste0(results_dir, "fmi_flag_melnychuk_allbad.png"), width = 7, height = 4.5, units = "in")

# Plot fuel subsidies only 
ggplot(fmi_flag_melnychuk_only)+
  aes(x = tot_fuel_subs/1e6, y = fmi_weighted, size = tot_landings/1e6, color = display_name)+
  geom_point()+
  geom_text_repel(aes(label = display_name), size = 4, force = 100, point.padding = 0.25, box.padding = 1)+
  theme_linedraw()+
  labs(x = "Total fuel subsidies (million 2018 $US)",
       y = "Weighted FMI")+
  scale_y_continuous(limits = c(0,1))+
  scale_x_continuous(labels = comma)+
  scale_size(range = c(2,8), breaks = c(5,10,15), limits = c(0,15), name = "Marine Capture Production (million mt, 2017)")+
  theme(legend.position = "top")+
  scale_color_discrete(guide = "none")

ggsave(paste0(results_dir, "fmi_flag_melnychuk_fuel.png"), width = 7, height = 4.5, units = "in")

```{r}
# For later use, get fraction of catch in each region from catch share fisheries, vs. not
# costello_catch_share_frac <- costello_2016_dat_edit %>%
#   group_by(region, catch_share) %>%
#   summarize(landings = sum(catch_new, na.rm = T)) %>%
#   ungroup() %>%
#   group_by(region) %>%
#   mutate(tot_landings = sum(landings, na.rm = T)) %>%
#   ungroup() %>%
#   mutate(frac_landings = landings/tot_landings) %>%
#   arrange(region)
```

>>>>

The purpose of this script is to assign management scores to all of our vessels, such that they can later be classified into different management regimes. The idea being that fisheries with effective management controls in place are less likely to see as large of changes in fishing effort resulting from subsidy reforms (e.g., Subsidies are likely to be less coupled with effort in well-managed fisheries; effort is instead likely dictated more by management).

@@

# Make figures?
make_plots <- T

@@

  # 3) Just FAO regions ---
  fao_areas <- read_sf(here::here("data", "shapefiles", "fao"), layer = "World_Fao_Zones")

@@

## Assign FMI indices to regions

@@

  # Map by EEZ/FAO area
  fmi_map <- ggplot()+
    geom_sf(data = world, fill = "black", color = "grey", size = 0.25)+
    geom_sf(data = fmi_map_dat, aes(fill = fmi_best), color = "grey", size = 0.25)+
    theme_bw()+
    scale_fill_distiller(palette = "YlGn", 
                         direction = 1,
                         limits = c(0.2, 1))+
    labs(fill = "FMI Score")+
    theme(plot.background = element_rect(color = NA),
          panel.border = element_rect(color = NA))

  fmi_map

  ggsave(paste0(results_dir, "fmi_score_map.png"), width = 7.5, height = 4, units = "in")
}
```

@@

# Median F/Fmsy by FAO region
median_fvfmsy_fao <- costello_2016_upsides_dat %>%
  group_by(region_fao_split) %>%
  summarize(fvfmsy_med_region = median(fv_fmsy, na.rm = T),
            fvfmsy_mean_region = mean(fv_fmsy, na.rm = T),
            fvfmsy_w_mean_region = weighted.mean(fv_fmsy, w = msy, na.rm = T)) %>%
  dplyr::select(fao_region = region_fao_split, fvfmsy_med_region, fvfmsy_mean_region, fvfmsy_w_mean_region)
```

  # Summarize data
    fvfmsy_map_dat <- fao_areas %>%
      rename(fao_region = zone) %>%
      left_join(median_fvfmsy_fao, by = "fao_region") %>%
      gather(metric, value, 3:5) %>%
      mutate(metric = str_replace(str_replace(metric, "fvfmsy_", ""), "_region", ""),
             metric_display = case_when(metric == "med" ~ "Median",
                                        metric == "w_mean" ~ "Weighted Mean",
                                        metric == "mean" ~ "Mean"))

  # Map by EEZ/FAO area
  fvfmsy_map <- ggplot()+
    geom_sf(data = world, fill = "black", color = "grey", size = 0.25)+
    geom_sf(data = fvfmsy_map_dat, aes(fill = value), color = "grey", size = 0.25)+
    theme_bw()+
    scale_fill_gradient2(low = "blue",
                         high = 'red',
                         mid = "white",
                         midpoint = 1,
                         limits = c(0,5),
                         oob = scales::squish)+
    labs(fill = "F/Fmsy")+
    theme(plot.background = element_rect(color = NA),
          panel.border = element_rect(color = NA))+
    facet_wrap(~metric_display, ncol = 1)

  fvfmsy_map

  ggsave(paste0(results_dir, "fvfmsy_map.png"), width = 7.5, height = 9.5, units = "in")
}
```

@@

# ```{r}
# prop_assessed_stocks <- costello_2016_upsides_dat %>%
#   group_by(region_fao_split) %>%
#   summarize(catch_ram = sum(catch[dbase == "RAM"]),
#             catch_other = sum(catch[dbase != "RAM"])) %>%
#   mutate(catch_prop_ram = catch_ram/(catch_ram + catch_other)) %>%
#   dplyr::select(fao_region = region_fao_split, catch_prop_ram)
# ```

@@

# ```{r}
# prop_catch_share_stocks <- costello_2016_upsides_dat %>%
#   group_by(region_fao_split) %>%
#   summarize(catch_share= sum(catch[catch_share == 1]),
#             catch_other = sum(catch[catch_share != 1])) %>%
#   mutate(catch_prop_cs= catch_share/(catch_share + catch_other)) %>%
#   dplyr::select(fao_region = region_fao_split, catch_prop_cs)
# ```

@@

```{r}
vessel_list_manage <- vessel_list_raw %>%
  left_join(eez_management_indices, by = c("eez_id")) %>%
  left_join(median_fvfmsy_fao, by = c("fao_region"))
  # left_join(prop_assessed_stocks, by = c("fao_region")) %>%
  # left_join(prop_catch_share_stocks, by = c("fao_region"))

# FAO region 18 is missing stock data, but has some effort
vessel_list_manage$fvfmsy_med_region[is.na(vessel_list_manage$fvfmsy_med_region)] <- 1
vessel_list_manage$fvfmsy_mean_region[is.na(vessel_list_manage$fvfmsy_mean_region)] <- 1
vessel_list_manage$fvfmsy_w_mean_region[is.na(vessel_list_manage$fvfmsy_w_mean_region)] <- 1

@@

fvfmsy_med_quantile <- tibble("indicator" = "fvfmsy_median") %>%
  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fvfmsy_med_region), nrow = 1)), names(quantile(vessel_list_manage$fvfmsy_med_region))))

fvfmsy_mean_quantile <- tibble("indicator" = "fvfmsy_mean") %>%
  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fvfmsy_mean_region), nrow = 1)), names(quantile(vessel_list_manage$fvfmsy_mean_region))))

fvfmsy_w_mean_quantile <- tibble("indicator" = "fvfmsy_w_mean") %>%
  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fvfmsy_w_mean_region), nrow = 1)), names(quantile(vessel_list_manage$fvfmsy_w_mean_region))))

indicator_quantiles <- fmi_quantile %>%
  bind_rows(fvfmsy_med_quantile) %>%
  bind_rows(fvfmsy_mean_quantile) %>%
  bind_rows(fvfmsy_w_mean_quantile)

@@

```{r}
# if(make_plots){
#   
#   # Summarize data
#   density_dat <- vessel_list_manage %>%
#     dplyr::select(fmi_best, fvfmsy_med_region, fvfmsy_mean_region, fvfmsy_w_mean_region)
#   
#   probs <- c(0, 1/3, 2/3, 1)
#   
#   # Make FMI density plot (across all vessels)
#   fmi_density <- density(density_dat$fmi_best)
#   
#   fmi_density_plot_dat <- data.frame(name = "FMI Score", x = fmi_density$x, y = fmi_density$y)
#  
#   fmi_quantiles <- quantile(fmi_density_plot_dat$y, prob=probs)
#   fmi_density_plot_dat$quant <- factor(findInterval(fmi_density_plot_dat$x, fmi_quantiles))
#   
#   fmi_density_plot <- ggplot(fmi_density_plot_dat, aes(x,y)) + 
#     geom_line() + 
#     geom_ribbon(aes(ymin=0, ymax=y, fill=quant)) + 
#     scale_y_continuous(expand = c(0,0)) + 
#     scale_fill_manual(labels = c("0-33%", "33-66%", "66-100%"), values = brewer.pal(3, "Blues"), name = "Quantile")+
#     labs(x = "FMI Score", y = "Kernal Density")+
#     theme_bw()
# 
#   # Make median F/Fmsy density plot (across all vessels)
#   med_density <- density(density_dat$fvfmsy_med_region)
# 
#   med_density_plot_dat <- data.frame(name = "Median F/Fmsy", x = med_density$x, y = med_density$y)
#   
#   med_quantiles <- quantile(med_density_plot_dat$y, prob=probs)
#   med_density_plot_dat$quant <- factor(findInterval(med_density_plot_dat$x, med_quantiles))
#   
#   med_density_plot <- ggplot(med_density_plot_dat, aes(x,y)) + 
#     geom_line() + 
#     geom_ribbon(aes(ymin=0, ymax=y, fill=quant)) + 
#     scale_y_continuous(expand = c(0,0)) + 
#     scale_fill_manual(labels = c("66-100%"), values = brewer.pal(3, "Blues")[3], name = "Quantile")+
#     labs(x = "Median F/Fmsy", y = "Kernal Density")+
#     theme_bw()
#   
#   # Make mean F/Fmsy density plot (across all vessels)
#   mean_density <- density(density_dat$fvfmsy_mean_region)
# 
#   mean_density_plot_dat <- data.frame(name = "Mean F/Fmsy", x = mean_density$x, y = mean_density$y)
#   
#   mean_quantiles <- quantile(mean_density_plot_dat$y, prob=probs)
#   mean_density_plot_dat$quant <- factor(findInterval(mean_density_plot_dat$x, mean_quantiles))
#   
#   mean_density_plot <- ggplot(mean_density_plot_dat, aes(x,y)) + 
#     geom_line() + 
#     geom_ribbon(aes(ymin=0, ymax=y, fill=quant)) + 
#     scale_y_continuous(expand = c(0,0)) + 
#     scale_fill_manual(labels = c("66-100%"), values = brewer.pal(3, "Blues")[3], name = "Quantile")+
#     labs(x = "Mean F/Fmsy", y = "Kernal Density")+
#     theme_bw()
#   
#   # Make weighted mean F/Fmsy density plot (across all vessels)
#   w_mean_density <- density(density_dat$fvfmsy_w_mean_region)
# 
#   w_mean_density_plot_dat <- data.frame(name = "Weight. Mean F/Fmsy", x = w_mean_density$x, y = w_mean_density$y)
#   
#   w_mean_quantiles <- quantile(w_mean_density_plot_dat$y, prob=probs)
#   w_mean_density_plot_dat$quant <- factor(findInterval(w_mean_density_plot_dat$x, w_mean_quantiles))
#   
#   w_mean_density_plot <- ggplot(w_mean_density_plot_dat, aes(x,y)) + 
#     geom_line() + 
#     geom_ribbon(aes(ymin=0, ymax=y, fill=quant)) + 
#     scale_y_continuous(expand = c(0,0)) + 
#     scale_fill_manual(labels = c("66-100%"), values = brewer.pal(3, "Blues")[3], name = "Quantile")+
#     labs(x = "Weight. Mean F/Fmsy", y = "Kernal Density")+
#     theme_bw()
#     
# }
```

```{r}
